ms2

### 2017-06-21 ms2/ms2.Rmd
bug groups

state_ineq = read_years('data/state_ineq_%i.tsv') %>%
  rename(cpb=mean) %>%
  group_by(state, drug_group) %>%
  summarize(cpb=mean(cpb), fnz=mean(fnz), nzg=mean(nzgini)) %>%
  ungroup()

hrr_ineq = read_years('data/hrr_ineq_%i.tsv') %>%
  rename(cpb=mean) %>%
  group_by(hrr, drug_group) %>%
  summarize(cpb=mean(cpb), fnz=mean(fnz), nzg=mean(nzgini)) %>%
  ungroup()
```

@@

uni_term = 'cpb' # univariable explanatory term
multi_term = 'nzg' # multivariable explanatory term (along with fnz)
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  bind_rows(
    linear_model(x, dep, uni_term) %>% mutate(model='uni'),
    linear_model(x, dep, c('fnz', multi_term)) %>% mutate(model='multi'),
    spearman_model(x, dep, uni_term) %>% mutate(model='spearman')
  ) %>%
    mutate(n_data=nrow(x))
}

>>>>

state_ineq = read_years('data/state_ineq_%i.tsv') %>%
  rename(cpb=mean, nzg=nzgini, nzr=mean_fnz_residual) %>%
  group_by(state, drug_group) %>%
  summarize_at(vars(-state, -drug_group, -total), mean) %>%
  ungroup()

hrr_ineq = read_years('data/hrr_ineq_%i.tsv') %>%
  rename(cpb=mean, nzg=nzgini, nzr=mean_fnz_residual) %>%
  group_by(hrr, drug_group) %>%
  summarize_at(vars(-hrr, -drug_group, -total), mean) %>%
  ungroup()
```

@@

uni_term = 'cpb' # univariable explanatory term
multi_term_adjuster = 'cpb'
multi_term = 'nb_prob' # multivariable explanatory term (along with fnz)
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  bind_rows(
    linear_model(x, dep, uni_term) %>% mutate(model='uni'),
    linear_model(x, dep, c(multi_term_adjuster, multi_term)) %>% mutate(model='multi'),
    spearman_model(x, dep, uni_term) %>% mutate(model='spearman')
  ) %>%
    mutate(n_data=nrow(x))
}
